SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-02 design_impl.tex
some comments

\item \textbf{Looking at L2 MSHR Queue while prefetching}\newline The original
  SPP does not consider the slots available in the L2 MSHR queue.  It has the
  assumption that at no time can the number of suggested prefetches
  exceed the capacity of the queue.  While it was not described in the paper, the
  internal confidence mechanism makes sure that the above assumption was maintained.  
  In PPF, since there cannot be an assumption on the degree of aggressiveness of the 
  underlying prefetcher, we explicitly check that at no point should the number 
  of suggested prefetches exceed the L2 MSHR queue.

@@

\subsection{Features used by Perceptron}
\label{Impl-Features}
Here we discuss the various features that correlate the prefetching decision
with the program behaviour.

>>>>

\item \textbf{Looking at L2 MSHR Queue while prefetching}\newline The
  original SPP does not consider the slots available in the L2 MSHR
  queue.  It has the assumption that at no time can the number of
  suggested prefetches exceed the capacity of the queue.  While it was
  not described in the paper, the internal confidence mechanism makes
  sure that the above assumption was maintained.  In PPF, since there
  cannot be an assumption on the degree of aggressiveness of the
  underlying prefetcher, we explicitly check that at no point should
  the number of suggested prefetches exceed the L2 MSHR queue. \pg{is
    this a big deal?  Seems like a detail}

@@

\subsection{Features used by Perceptron}
\label{Impl-Features}
Here we discuss the various features that correlate the prefetching
decision with the program behavior. \pg{again you want to get at why
  these were chosen.  Also mention that you searched over a large
  space of possible features and these were the best.}
